Joint analysis of read count data

### 2020-09-09 combined_analysis/combine_all_data.Rmd
add zenith

>>>>

```{r gene_set_test.marginal}
res_zenith_DxSex.GO = run_zenith( fit_interaction_DxSex, colnames(L), gs.GO.collection )
res_zenith_DxSex.MSigDB = run_zenith( fit_interaction_DxSex, colnames(L), gs.MSigDB.collection )
```

```{r show.gene_set_test.marginal}
show_zenith_results( res_zenith_DxSex.GO, "Scz")
show_zenith_results( res_zenith_DxSex.MSigDB, "Scz")

show_zenith_results( res_zenith_DxSex.GO, "BP")
show_zenith_results( res_zenith_DxSex.MSigDB, "BP")

show_zenith_results( res_zenith_DxSex.GO, "Sex")
show_zenith_results( res_zenith_DxSex.MSigDB, "Sex")
```
